To log or not to log

### 2022-11-15 main.tex
Addressing comments before larger restructuring

Log transforming forecasts and observations shifts the focus of the evaluation while preserving propriety of the score. Instead of scoring the magnitude of absolute errors this approach captures relative errors and is approximately equivalent to scoring a forecast for the growth rate of the observed quantity.

We focus on the log transformation, as it represents a convenient way of achieving our goal of evaluating how well a forecast captures the growth dynamic inherent to epidemiological process.

Applying the log transformation, among other transformations, is permissible because it is a strictly monotonic transformation.

While rankings between different models may indeed change, even for a single forecast, the relevant condition for a scoring rule to be strictly proper is still satisfied: In expectation a forecaster will receive the best score if she reports a predictive distribution that is equal to the data-generating distribution, even after transforming both the forecasts and the observations (representing draws from the data-generating distribution).

It is important to first apply the transformation and then score the transformed forecasts and observations. Simply taking the log of the WIS or the CRPS computed on the natural scale, i.e. computing $\log S(x, y)$ results in an improper score and is therefore not advised. This is because the logarithm of the WIS / CRPS does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

@@

Overall model rankings usually differ even more when performance is averaged across multiple forecasts. This effect is not mainly driven by the kinds of changes in model rankings for single forecasts we just discussed. Rather, as observations from exponential processes are likely to be on very different absolute scales, large observations will account for the majority of absolute score but will not dominate relative scores in the same way. When aggregating scores across metrices with different scales, for example reported cases, and hospitalisations even an ideal forecaster will make much larger errors when predicting a quantity such as reported case numbers, than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log transforming forecasts and observations may also result in the opposite extreme, since small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This is especially true when forecasts are restricted to discrete values. 
Whether or not forecast targets with smaller quantities receive higher scores than those for targets with larger quantities, depends on the exact relationship between the mean and the variance of the quantity of interest.

@@

@@

As expected on the natural scale, scores correlate strongly (XX) with the average number of observed cases / deaths in a given country (see Fig \ref{fig:HUB-mean-locations}A, B) and this relationship is not evident on the log scale. Interestingly, there is some evidence a negative relationship between the mean number of observations in a country and score when evaluated on a log scale implying that countries with lower mean incidence may be harder to forecast.

>>>>

The goal of log transforming forecasts and observations is to shift the focus of the evaluation while preserving the propriety of the score. Instead of a score representing the magnitude of absolute errors this approach allows to obtain a score which measures relative error and provides an approximate measure for how well a forecast captures the multiplicative growth rate of the target quantity. In this paper we focus on the log transformation, but note that many other transformations may be useful and appropriate (see section XXXX) .

The log transformation is permissible (in the sense that it preserves propriety of the score), because it is a strictly monotonic transformation. Even though actual rankings between models may change, a forecaster will in expectation still minimise her score if she reports a predictive distribution that is equal to the data-generating distribution. The order of the operations matters, and applying the log transformation after scores have been computed, i.e. computing $\log S(x, y)$ results in an improper score. This is because taking the logarithm of the WIS / CRPS results in a score that does not penalise outliers enough and therefore incentivises overconfident predictions. We illustrate this point using simulated data in Figure \ref{fig:log-improper}, where it can easily be seen that overconfident models perform best in terms of the log WIS.

@@

Overall model rankings usually differ even more when performance is averaged across multiple forecasts. This effect is not mainly driven by the kinds of changes in model rankings for single forecasts we just discussed. Rather, as observations from exponential processes are likely to be on very different absolute scales, large observations will account for the majority of absolute score but will not dominate relative scores in the same way. When aggregating scores across metrics with different scales, for example reported cases, and hospitalisations, even an ideal (i.e. perfect) forecaster will make much larger errors when predicting case numbers than when predicting hospitalisations. Evaluating forecasts based on relative errors may help with comparing performance across different targets. However, log transforming forecasts and observations may also result in the opposite extreme, since small absolute errors (e.g. predicting 9, rather than 3 deaths) may be large in relative terms if the quantity to forecast is very small. This is especially true when forecasts are restricted to discrete values.

@@

Whether or not forecast targets with smaller quantities receive higher scores than those for targets with larger quantities, depends on the exact relationship between the mean and the variance of the quantity of interest.

@@

As expected on the natural scale, scores correlate strongly (XX) with the average number of observed cases / deaths in a given country (see Fig \ref{fig:HUB-mean-locations}A, B).
This relationship is not evident on the log scale, where correlation is much weaker and maybe slightly negative, implying larger scores for for countries with lower mean incidences.
